---
title             : "Have federal agencies become more partisan over time?"
shorttitle        : "Do members of Congress have an increasing level of influence on the outcome of federal agency financial rulemaking?"

author: 
  - name          : "Samiha Bhushan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"


affiliation:
  - id            : "1"
    institution   : "University of Wisconsin-Madison"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
I will gather data from 40 rules issued by financial agencies, including but not limited
to the Consumer Financial Protection Bureau, the Treasury Department, and the Office of
the Comptroller of the Currency. I focus on public comments issued by members of
Congress and focus on whether their demands were ultimately fulfilled in the final rule.
The research design additionally combines data from a previous study conducted by
Jennifer L. Selin, who determined an estimate of the level of structural independence for
several agencies during the Obama administration. My study will also include rules during
the subsequent Trump administration, wherein the Senate majority switched to the
Republican party. I will compare and contrast rules from both eras to determine if
influence from political parties have grown over time, including determining if there is an
increased presence of politicians commenting on policies.
I will also use textual analysis in addition to the hand coding to see if elected officials
use more partisan rhetoric over time. In this study, “partisan rhetoric” refers to an
individual making positive assertions about their own party or negative assertions about
the opposing party. I will also examine whether the demands of elected officials that are
the same party as the President are increasingly met over those of the opposing party.

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results


install.packages('gsheet')
library(gsheet)
gsheet2tbl('https://docs.google.com/spreadsheets/d/1HBjG32qWVdf9YxfGPEJhNmSw65Z9XzPhHdDbLnc3mYc/edit?usp=sharing')

install.packages("googlesheets4")
library(googlesheets4)
congress_data <- read_sheet("https://docs.google.com/spreadsheets/d/1HBjG32qWVdf9YxfGPEJhNmSw65Z9XzPhHdDbLnc3mYc/edit?usp=sharing")

congress_data[!(is.na(congress_data$success) | congress_data$success==""), ]
# select variables v1, v2, v3
myvars <- c("docket_id","submitter_name", "position", "success")
newdata <- congress_data[myvars]
clean_congress <- newdata[!(is.na(newdata$success) | newdata$success==""), ]

library(stringr)
library(dplyr)
financial_rules <- c("CFPB", "OCC", "IRS")
cfpbSubset <- clean_congress[grep("CFPB", clean_congress$docket_id), ]
cfpbSubset

congresult <- filter(clean_congress, grepl(paste(financial_rules, collapse="|"), docket_id))
congresult

summary(cfpbSubset)

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
