---
title: "Have federal agencies become more partisan over time?"
author:
- name: Samiha Bhushan
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: my@email.com
shorttitle: Do members of Congress have an increasing level of influence on the outcome
  of federal agency financial rulemaking?
output:
  html_document:
    df_print: paged
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  O
keywords: keywords
wordcount: X
bibliography: r-references.bib
floatsintext: no
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: University of Wisconsin-Madison
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
I will gather data from 40 rules issued by financial agencies, including but not limited
to the Consumer Financial Protection Bureau, the Treasury Department, and the Office of
the Comptroller of the Currency. I focus on public comments issued by members of
Congress and focus on whether their demands were ultimately fulfilled in the final rule.
The research design additionally combines data from a previous study conducted by
Jennifer L. Selin, who determined an estimate of the level of structural independence for
several agencies during the Obama administration. My study will also include rules during
the subsequent Trump administration, wherein the Senate majority switched to the
Republican party. I will compare and contrast rules from both eras to determine if
influence from political parties have grown over time, including determining if there is an
increased presence of politicians commenting on policies.
I will also use textual analysis in addition to the hand coding to see if elected officials
use more partisan rhetoric over time. In this study, “partisan rhetoric” refers to an
individual making positive assertions about their own party or negative assertions about
the opposing party. I will also examine whether the demands of elected officials that are
the same party as the President are increasingly met over those of the opposing party.

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

```{r}
library(gsheet)
gsheet2tbl('https://docs.google.com/spreadsheets/d/1HBjG32qWVdf9YxfGPEJhNmSw65Z9XzPhHdDbLnc3mYc/edit?usp=sharing')

#install.packages("googlesheets4")
library(googlesheets4)
congress_data <- read_sheet("https://docs.google.com/spreadsheets/d/1HBjG32qWVdf9YxfGPEJhNmSw65Z9XzPhHdDbLnc3mYc/edit?usp=sharing")

#finding financial rules
#congress_data[!(is.na(congress_data$success) | congress_data$success==""), ]
# select variables v1, v2, v3
myvars <- c("docket_id","submitter_name", "position", "success")
newdata <- congress_data[myvars]
#removing rows with no success coded
clean_congress <- newdata[!(is.na(newdata$success) | newdata$success==""), ]
clean_congress

#creating new dataset with financial agencies and estimates
library(stringr)
library(dplyr)
financial_rules <- c("CFPB", "OCC", "IRS", "TREAS", "FTC")
cfpbSubset <- clean_congress[grep("CFPB", clean_congress$docket_id), ]
occSubset <- clean_congress[grep("OCC", clean_congress$docket_id), ]
irsSubset <- clean_congress[grep("IRS", clean_congress$docket_id), ]
treasSubset <- clean_congress[grep("TREAS", clean_congress$docket_id), ]
ftcSubset <- clean_congress[grep("FTC", clean_congress$docket_id), ]

congresult <- filter(clean_congress, grepl(paste(financial_rules, collapse="|"), docket_id))
congresult

avg_success <- c(mean(cfpbSubset$success), mean(occSubset$success), mean(irsSubset$success), mean(treasSubset$success), mean(ftcSubset$success))
avg_success

library(readxl)
federal_agencies <- read_excel("/Users/samihabhushan/Documents/financial/federal_agencies_estimate.xlsx")
federal_agencies_estimate <- c(federal_agencies$Estimate)
federal_agencies_estimate

# merge two data frames by ID
fed_id <- merge(avg_success,federal_agencies)


federal_agencies_table <- read_excel("/Users/samihabhushan/Documents/financial/federal_agencies_merged.xlsx")

summary(federal_agencies_table)

cor(federal_agencies_table$Estimate, federal_agencies_table$Avg_Success)

plot(Estimate ~ Avg_Success, data=federal_agencies_table)

fed_estim.lm <- lm(Estimate ~ Avg_Success, data=federal_agencies_table)

regression_fed <- summary(fed_estim.lm)
```


Running a multiple regression analysis on the overall average success and independence estimates, the correlation between the level of independence of federal agencies and average success overall for combined rules, the correlation coefficient is 'r cor(federal_agencies_table$Estimate, federal_agencies_table$Avg_Success)' and the r-squared value is 0.0043, suggesting that the 0.43% of variation in success is explained by agency's level of independence. 

```{r}
#formatting merged datasets
knitr::kable(head(federal_agencies_table), "pipe")
plot(federal_agencies_table)

regression_fed <- summary(fed_estim.lm)

apa_table(
federal_agencies_table
, caption = "Descriptive statistics of federal independence by agencies."
, note = "avg success vs agencies"
)
```


# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

